Dynamic Prediction of Non-Guassian Outcome with fast Generalized Functional Principal Analysis

### 2023-03-15 Write-ups/Manuscript.Rmd
solve AUC error

```{r}
runtime
# calculate ISE on binned grid
ise_mat <- matrix(NA, nrow = M, ncol = 4) # row index iteration, col index max observation time
colnames(ise_mat) <- c("t200", "t400", "t600", "t800")

@@

  ise_mat[m, ] <- ise_m
}
```
```{r}
# calculate AUC on unbinned grid
auc_mat <- matrix(NA, nrow = M, ncol = 4) # row index iteration, col index max observation time
colnames(auc_mat) <- c("t200", "t400", "t600", "t800")

@@

    t <- t_vec[i]
    # predicted value
    pred_name <- paste("pred_t", t, sep = "")
    pred_mat <- pred_lst[[m]] %>% select(id, bin, all_of(pred_name)) %>% 
      pivot_wider(names_from = id, values_from = pred_name) %>%
      column_to_rownames("bin")
    pred_full <- sapply(1:N,
                           function(x){approx(x=mid, y=pred_mat[ , x], xout = 1:J)$y})
    pred_full <- exp(pred_full)/(1+exp(pred_full))
    row_id <- complete.cases(pred_full)
    auc_perf <- performance(prediction(pred_full[row_id, ], Y_mat[row_id, ]), "auc")
    auc_mat[m, i] <- mean(unlist(auc_perf@y.values))
  }

@@

auc_mat
```

>>>>

```{r}
mean(runtime)
# calculate ISE on binned grid
ise_mat <- matrix(NA, nrow = M, ncol = 4) # row index iteration, col index max observation time
colnames(ise_mat) <- c("t200", "t400", "t600", "t800")

@@

  ise_mat[m, ] <- ise_m
}

```{r}
# calculate AUC on unbinned grid
auc_mat <- matrix(NA, nrow = M, ncol = 4) # row index iteration, col index max observation time
colnames(auc_mat) <- c("t200", "t400", "t600", "t800")

skip_count <- 0

@@

    t <- t_vec[i]
    # predicted value
    pred_name <- paste("pred_t", t, sep = "")
    pred_mat <- pred_lst[[m]] %>% select(id, bin, all_of(pred_name)) %>% 
      pivot_wider(names_from = id, values_from = all_of(pred_name)) %>%
      column_to_rownames("bin")
    pred_full <- sapply(1:N,
                           function(x){approx(x=mid, y=pred_mat[ , x], xout = 1:J)$y})
    pred_full <- exp(pred_full)/(1+exp(pred_full))
    row_id <- complete.cases(pred_full)

    # calculate AUC, skip subjects with no variation in outcome Y
    auc_lst <- lapply(1:N, function(x){
      auc_try <- try(performance(prediction(pred_full[row_id, x], Y_mat[row_id, x]), "auc"), 
                     silent = T)
      auc_pref <- ifelse(class(auc_try)=="try-error",NA, auc_try@y.values)
      return(auc_pref)               
    })

    auc_mat[m, i] <- mean(unlist(auc_lst), na.rm = T)
    skip_count <- skip_count+sum(is.na(auc_lst))
  }

@@
